Geometric variational problems

### 2020-11-16 NSF2020/Description/background.tex

\noindent
{\bf Collaborative Research: Mathematical modeling and simulation of
self-assembling amphiphilic particles in solvent} \\
%{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
{\em Rolf Ryham (lead PI, Fordham University), Bryan Quaife (PI,
Florida State University), and Young-Nan Young (PI, New Jersey Institute of Technology)}
\section{Background}
\label{sec:background}
The goal of this collaborative proposal is to use mathematical modeling
and numerical simulations to investigate the dynamic self-assembly of
amphiphilic particles interacting via hydrophobic forces
in solvent. Amphiphilic particles (such as lipid molecules) possess
both hydrophobic and hydrophilic structures. In a viscous solvent they
self-assemble into meso-/macroscopic structures (such as micelles and
bilayers of lipids) to shield their hydrophobic parts from contact with
the solvent (water) molecules.
%
%\subsection{Hydrophobic Forces}
%\label{sec:hydrophobicforce}
%
Such self-assembly of amphiphiles via hydrophobic forces is ubiquitous in biology and biophysics \cite{Israelachvili1954},
%The hydrophobic force is a ubiquitous molecular interaction in biology \cite{Israelachvili1954}, 
and has been a major source of nonspecific interactions between
nanoparticles in soft matter
\cite{Sanchez-IglesiasEtAl2012_ACSNano,AltantzisEtAl2013_PSC,XieYangLuEtAl2020_COCIS}. 
%The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles so to design smart materials of desirable properties by
%tuning the geometry and properties of the amphiphilic particles.

>>>>

\noindent
{\bf Collaborative Research: Mathematical modeling and simulation of
self-assembling amphiphilic particles in solvent} \\
%{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
{\em Rolf Ryham (lead PI, Fordham University), Bryan Quaife (PI,
Florida State University), and Yuan-Nan Young (PI, New Jersey Institute of Technology)}
\section{Background}
\label{sec:background}
The goal of this collaborative proposal is to use mathematical modeling
and numerical simulations to investigate the dynamic self-assembly of
amphiphilic particles interacting via hydrophobic forces
in solvent. Amphiphilic particles (such as lipid molecules) possess
both hydrophobic and hydrophilic structures. In a viscous solvent they
self-assemble into meso-/macroscopic structures (such as micelles and
bilayers of lipids) to shield their hydrophobic parts from contact with
the solvent (water) molecules.
%
%\subsection{Hydrophobic Forces}
%\label{sec:hydrophobicforce}
%
Such self-assembly of amphiphiles via hydrophobic forces is ubiquitous in biology and biophysics \cite{Israelachvili1954},
%The hydrophobic force is a ubiquitous molecular interaction in biology \cite{Israelachvili1954}, 
and has been a major source of nonspecific interactions between
nanoparticles in soft matter
\cite{Sanchez-IglesiasEtAl2012_ACSNano,AltantzisEtAl2013_PSC,XieYangLuEtAl2020_COCIS}. 
%The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles so to design smart materials of desirable properties by
%tuning the geometry and properties of the amphiphilic particles.
